\urlstyle{same}
% \thispagestyle{plain}
\begin{thebibliography}{60}
\addcontentsline{toc}{chapter}{Bibliography}

    \bibitem{YR} R. Abdul Khalek et al., "Science Requirements and Detector Concepts for the Electron-Ion Collider: EIC Yellow Report," \textit{Nuclear Physics A}, vol. 1026, a. 122447, October 2021. [Online]. Available: \url{https://doi.org/10.1016/j.nuclphysa.2022.122447}. [Accessed: 20-Dec-2023].

    \bibitem{wiki} ePIC Collaboration, "ePIC Experiment Wiki," \textit{wiki.bnl.gov}, 2024. [Online]. Available: \url{https://wiki.bnl.gov/EPIC/index.php?title=Main_Page}. [Accessed: 27-Feb-2024].

    \bibitem{rhic} Brookhaven National Laboratory, "Relativistic Heavy Ion Collider webpage," \textit{www.bnl.gov}, 2024. [Online]. Available: \url{https://www.bnl.gov/rhic}. [Accessed: 23-Jul-2024].

    \bibitem{whitepaper} A. Accardi et al., "Electron-Ion Collider: The next QCD frontier," \textit{The European Physical Journal A}, vol. 52, a. 268, 2016. [Online]. Available: Springer Link, \url{http://www.springer.com} [Accessed: 20-Dec-2023].

    \bibitem{CDR} U.S. Department of Energy, "Electron Ion Collider Conceptual Design Report 2021," \textit{technical report}, 2021. [Online] Available: \url{https://doi.org/10.x2172/1765663}. [Accessed: 05-Apr-2024].

    \bibitem{grupen_wigmans} R. Wigmans, "Calorimetry," in \textit{Handbook of Particle Detection and Imaging}, C. Grupen and I. Buvat, Eds. Berlin, Heidelberg: Springer, 2012, pp. 497-517. [Online]. Available: \url{https://doi.org/10.1007/978-3-642-13271-1_20}. [Accessed: 12-Apr-2024].

    \bibitem{livan_calorimetry} M. Livan and R. Wigmans, \textit{Calorimetry for Collider Physics, an Introduction}. Cham: Springer, 2019. 

    \bibitem{grupen_particle-detectors} C. Grupen and B. A. Shwartz, \textit{Particle Detectors}. 2nd ed. Cambridge: Cambridge University Press, 2008.

    \bibitem{hanagaki} K. Hanagaki, J. Tanaka, M. Tomoto and Y. Yamazaki, "Particle Identification," in \textit{Experimental Techniques in Modern High-Energy Physics: A Beginner‘s Guide}, K. Hanagaki, J. Tanaka, M. Tomoto and Y. Yamazaki, Eds. Tokyo: Springer. 2022, pp. 69-114. [Online]. Available: \url{ https://doi.org/10.1007/978-4-431-56931-2_6}. [Accessed: 12-Apr-2024].

    \bibitem{lippmann} Ch. Lippmann, "Particle Identification," \textit{Nuclear Instruments and Methods in Physics Research Section A: Accelerators, Spectrometers, Detectors and Associated Equipment}, vol. 666, pp. 148-172, February 2012. [Online]. Available: \url{https://doi.org/10.1016/j.nima.2011.03.009}. [Accessed: 12-Apr-2024].

    \bibitem{dd4hep} M. Frank, F. Gaede, M. Petric and A. Sailer, "DD4hep webpage" \textit{dd4hep.web.cern.ch}, 2023. [Online] Available: \url{https://dd4hep.web.cern.ch/}. [Accessed: 02-May-2024].

    \bibitem{DD4hepManual} M. Frank, F. Gaede, M. Petric and A. Sailer, "DD4hep User Manual," July 24, 2024. [Online] Available: \url{https://dd4hep.web.cern.ch/dd4hep/usermanuals/DD4hepManual/DD4hepManual.pdf}. [Accessed: 02-Jun-2024].

    \bibitem{JANA2} D. Lawrence, A. Boehnlein, N. Brei and D. Romanov, "JANA2: Multithreaded Event Reconstruction," \textit{Journal of Physics: Conference Series}, vol. 1525, a. 012032, 2020. [Online] Available: \url{https://dx.doi.org/10.1088/1742-6596/1525/1/012032}. [Accessed: 02-Jul-2024].

    \bibitem{eicrecon_page} "EICrecon webpage," [Online]. Available: \url{https://eic.github.io/}. [Accessed: 23-May-2024].

    \bibitem{hepmc3} A. Buckley et al., "The HepMC3 event record library for Monte Carlo event generators," \textit{Computer Physics Communications}, vol. 260, a. 107310, March 2021. [Online]. Available: \url{https://doi.org/10.1016/j.cpc.2020.107310}. [Accessed: 02-Jul-2024].

    \bibitem{podio} AIDAsoft, "podio GitHub repository," \textit{github.com}, 2024. [Online]. Available: \url{https://github.com/AIDASoft/podio}. [Accessed: 22-Jul-2024].
     
\end{thebibliography}
